TODO LIST

### 2019-01-22 LMCS/sendrev/todo-list.tex
un par de typos
correcciones Reviewer 2

@@

\item p.32/33, example 6.2: I don't see why the formula given for dag's does not work for arbitrary

@@

@@

	\item p.1, footnote: ``clases'' should be ``classes''

@@

@@

@@

	\item p.30: ``to define a natural generalization for functions of the notion of least fixed point of

@@

	\item In [1], a similar hierarchy to the one by Saluja et al. was introduced and studied. This work
	should be cited.

@@

\item For the most involved proofs, you could describe informally your proof strategy in a few lines to help the reader. You may also add some example to illustrate the different fragment of QSO (you already do it sometimes and it is very helpful).

\item[$\checkmark$] page 4:
-some of the $\to$ some of them 
\item[$\checkmark$] page 10: 
-$2^{|A|^l}$-bits $\to$ $2^{|A|^l}$ bits
\item[$\checkmark$] page 21:
-it does not mentioned $\to$ it does not mention
\item[$\checkmark$] page 22: 
-you make a long proof about some closure under subtraction by one.
You should put the result in a theorem envirpnment to make what you are
proving more evident.
\item[$\checkmark$] -replace .... for $\to$ replace ... by;  there are several instances of
that
\item[$\checkmark$] -$\phi$ is an FO-formula $\to$ a $\Sigma_1[FO]$ formula
\item -you explain that you rewrite your formula to obtain conditions a,b and c, 
you should give an idea how these conditions will be used
\item[$\checkmark$] page 23:
a SO, a FO  an SO, an FO
\item page 24: 
if, if $\phi$$\to$ $\phi$
\item page 25: 
-you explain that the proof relies on witnesses of logarithmic size.
It was not clear to me while reading the proof. Can you explain more ?
\item page 28:
-the complete problem for $\Sigma$ QSO($\Sigma_2$ Horn) would be complete also for $\#\Sigma-2$ Horn. You should mention here that you do not need sum here
and that the framework of [39] is enough for this result.
\item[?] page 30: ``this notion can be used to captures FP'' $\to$ ``... to capture FP''

\item[$\checkmark$] page 32: 
- paths of length at most n $\to$ in an acylic graph, all paths are of size less than n
\item page 33:
-there is a proof symbol \verb|\qed| but it does not end a well defined proof environment

\item page 38: 
the last sentence on fixed point operator is to vague. Either expand it to 
say what king of question on fixed point operator you want to investigate or remove it	
\end{itemize}

>>>>

\martin{no logr\'e completar esta correcci\'on}

@@

\item[?] p.32/33, example 6.2: I don't see why the formula given for dag's does not work for arbitrary

@@

\martin{me gustar\'ia tener feedback para saber si mi correcci\'on est\'a bien}

@@

	\item[$\checkmark$] p.1, footnote: ``clases'' should be ``classes''

@@

	\martin{no alcanc\'e a revisar esta ni la de cuatro puntos m\'as adelante}

@@

	\martin{lo que menciono arriba}

@@

	\item[$\checkmark$] p.30: ``to define a natural generalization for functions of the notion of least fixed point of

@@

	\item In [1], a similar hierarchy to the one by Saluja et al. was introduced and studied. This work should be cited.

@@

\item For the most involved proofs, you could describe informally your proof strategy in a few lines to help the reader. You may also add some example to illustrate the different fragment of QSO (you already do it sometimes and it is very helpful).
\martin{me gustar\'ia que conversemos qu\'e demostraciones necesitan esto, y si el outline de la demostraci\'on de -1 basta. Tambi\'en qu\'e fragmentos de QSO necesitan un ejemplo.}

\item[$\checkmark$] page 4:
-some of the $\to$ some of them 
\item[$\checkmark$] page 10: 
-$2^{|A|^l}$-bits $\to$ $2^{|A|^l}$ bits
\item[$\checkmark$] page 21:
-it does not mentioned $\to$ it does not mention
\item[$\checkmark$] page 22: 
-you make a long proof about some closure under subtraction by one.
You should put the result in a theorem envirpnment to make what you are
proving more evident.
\item[$\checkmark$] -replace .... for $\to$ replace ... by;  there are several instances of
that
\item[$\checkmark$] -$\phi$ is an FO-formula $\to$ a $\Sigma_1[FO]$ formula
\item[$\checkmark$] -you explain that you rewrite your formula to obtain conditions a,b and c, 
you should give an idea how these conditions will be used
\item[$\checkmark$] page 23:
a SO, a FO  an SO, an FO
\item[$\checkmark$] page 24: 
if, if $\phi$$\to$ $\phi$
\item page 25: 
-you explain that the proof relies on witnesses of logarithmic size.
It was not clear to me while reading the proof. Can you explain more ?
\martin{no logr\'e corregir esto, es la misma acotaci\'on que el Reviewer 1}
\item page 28:
-the complete problem for $\Sigma$ QSO($\Sigma_2$ Horn) would be complete also for $\#\Sigma-2$ Horn. You should mention here that you do not need sum here
and that the framework of [39] is enough for this result.
\martin{conversemos esto}
\item[$\checkmark$] page 30: ``this notion can be used to captures FP'' $\to$ ``... to capture FP''

\item[$\checkmark$] page 32: 
- paths of length at most n $\to$ in an acylic graph, all paths are of size less than n
\item[$\checkmark$] page 33:
-there is a proof symbol \verb|\qed| but it does not end a well defined proof environment

\item page 38: 
the last sentence on fixed point operator is to vague. Either expand it to 
say what king of question on fixed point operator you want to investigate or remove it	
\martin{conversemos esto}
\end{itemize}
